A neural coarse graining theory of consciousness/\newline Non-trivial Informational closure through neural coarse-graining as the Fundamental Informational Correlates of Consciousness

### 2019-05-06 Paper_neural_coarse_graining_of_consciousness.tex
Updates from Overleaf

%% ============================== Useful packages ============================= %
\usepackage[dvipsnames,table,xcdraw]{xcolor}
\usepackage[round]{natbib}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{authblk}
\usepackage{float}
\usepackage{tikz}

@@

	\section{Conscious versus Unconscious Processing}

\rlstart{3}	
		\ideaBox{The goal of this part is to combine empirical study and phenomenology}
	    \ideaBox{I need to expend this section much more and more references}
	    In this section, we suggest that our theory has a strong exploratory and predictive power but with minimal assumptions.  
		Our theory indicates that, to make information conscious, a sufficient and a necessary conditions need to be satisfied.

@@

		\subsection{Unconscious Processing}
		\begin{ants}
		    @ As described above, if information processing fails to meet either one of the two necessary conditions, information remains unconscious.

		    @ First, considering processes which fail to meet the first condition. That is, a information process is not NTIC. We can see many processes in the neural network system fall in this category.

		    @ In this category, processes cannot form NTIC. The internal states of the processes are partially or fully determined by environment states, i.e. information is not closed. Reflective behaviours are one of the main subcategory.

		    @Reflective behaviours usually are considered as automatic and non-conscious behavioural controls. \citep{casali2013theoretically}\needref{More referene}.

@@

>>>>

%% ============================== Useful packages ============================= %
\usepackage[dvipsnames,table,xcdraw]{xcolor}
\usepackage[round]{natbib}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{svg}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{authblk}
\usepackage{float}
\usepackage{tikz}

@@

	\section{Conscious versus Unconscious Processing}
		\ideaBox{The goal of this part is to combine empirical study and phenomenology}
	    \ideaBox{I need to expend this section much more and more references}
	    In this section, we suggest that our theory has a strong exploratory and predictive power but with minimal assumptions.  
		Our theory indicates that, to make information conscious, a sufficient and a necessary conditions need to be satisfied.

@@

		\subsection{Unconscious Processing}
\rlstart{3}			
		    \subsubsection{\sim 1}
		    % reflexive behaviour
    		\begin{figure}[H]
    			\includegraphics[width=0.8\textwidth]{WritingMaterials/Fig_Reflexive/Reflexive.pdf}
    			\caption{Reflexive Behaviours}
    			\label{fig:reflexive}
    		\end{figure}

    		\begin{ants}
    		    @ As described above, if a process fails to meet either one of the two necessary conditions, information remains unconscious.

    		    @ We first consider the first condition: A process fails to achieve NTIC.

    		    @ Many processes in the neural network system fall in this category.

    		    @ When a process is not information closed the internal state of the process is largely determined by the environmental state.

    		    @ In terms of perception, this indicates that the process only passively reacts.

    		    @ In terms of action, this implies reflective behaviours.

    		    @ Reflective behaviours usually are considered as automatic and non-conscious behavioural controls. \citep{casali2013theoretically}\needref{More referene}.

@@

    		\end{ants}
\rlend
